Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-08-17 write-up/covid-writeup.tex
ifr in writeup - need more model details

\def\pr{\text{pr}}
\def\sgn{\text{sgn}}
\def\I{\bf I}

@@

>>>>

\def\pr{\text{pr}}
\def\sgn{\text{sgn}}
\def\I{\bf I}
\def\code#1{\texttt{#1}}

@@

We fit the

\begin{align*}
\frac{\partial s_t}{\partial t} &= - \beta s_t i_t; \quad \frac{\partial e_t}{\partial t} = \beta_t s_t i_t - \sigma e_t; \quad \\
\frac{\partial i^{(T)}_t}{\partial t} &= \sigma e_t - \gamma i_t; \quad
\frac{\partial r_t}{\partial t} = - \gamma i_t.
\end{align*}

We allow $\beta_t$ to be time-varying to account for the

"2020-03-23", "2020-06-15", "2020-10-01".

$w_t = 1/ \left( 1 + \exp \left( - \xi (t - t_1 - \nu)  \right) \right)$

We defined a weight $w^{(1)}_t = 1$ prior to time $t_1$ and goes to $1$ as $t \to \infty$

to accoun tfor

$\beta (1-w_t) + \eta weight$

For simplicity, we list the priors used in STAN below:
\begin{itemize}
  \item \code{beta $\sim$ Normal(1.5, 1) T[0,];}
  \item \code{gamma $\sim$ normal(0.3, 0.5) T[0,];}
  \item \code{sigma $\sim$ normal(0.4, 0.5) T[0,];}
  \item \code{phi\_inv $\sim$ exponential(5);}
  \item \code{i0 $\sim$ normal(0, 10);}
  \item \code{e0 $\sim$ normal(0, 10);}
  \item \code{eta $\sim$ normal(1, 1) T[0,];}
  \item \code{eta\_two $\sim$ normal(1, 1) T[0,];}
  \item \code{eta\_three $\sim$ normal(1, 1) T[0,];}
  \item \code{nu $\sim$ exponential(1./5);}
  \item \code{nu\_two $\sim$ exponential(1./5);}
  \item \code{nu\_three $\sim$ exponential(1./5);}
  \item \code{xi\_raw $\sim$ beta(1, 1);}
  \item \code{phi = 1/phi\_inv;}
  \item \code{xi = xi\_raw + 0.5;}
\end{itemize}

\begin{figure}[!th]
\centering
 \includegraphics[width=.9\linewidth]{../figs/logifr.png}
 \caption{Logarithm of Infection Fatality Rate (IFR) by Age.  Linear model on the log-scale fits well and allows us to extrapolate publicly-reported IFR numbers to entire age range.}
 \label{fig:logifr}
\end{figure}
